---
title: "GMSP Indicators"
output: 
  flexdashboard::flex_dashboard:
    orientation: rows
    vertical_layout: fill
---

```{r setup, include=FALSE}
#install.packages("ggplot2")
#install.packages("tidyverse")
#install.packages("plotly")
#install.packages("ggplotly")
library(flexdashboard)
library(ggplot2)
library(tidyverse)
library(plotly)
#library(ggplotly)


cca_data_p1 <- read.csv("C:/Users/Clayton.Adamson/GREATER MSP/Research & Intelligence - Documents/Major projects/Regional Indicators Dashboard/2023/cca_temp/cca_data_v1.csv") %>%
  select(-X, -NAESTIMATES, -RK2015, -RK2016, -RK2017, -RK2018, -RK2019, -RK2020,
         -RK2021, -RK2022, -RK2023) %>%
  gather(year, value, c(NA2015, NA2016, NA2017, NA2018, NA2019, NA2020, NA2021, 
                        NA2022, NA2023)) %>%
  mutate(year = substr(year,3,6))
cca_data_p2 <- read.csv("C:/Users/Clayton.Adamson/GREATER MSP/Research & Intelligence - Documents/Major projects/Regional Indicators Dashboard/2023/cca_temp/cca_data_v1.csv") %>%
  select(-X, -NAESTIMATES, -NA2015, -NA2016, -NA2017, -NA2018, -NA2019, -NA2020,
         -NA2021, -NA2022, -NA2023) %>%
  gather(year, rank, c(RK2015, RK2016, RK2017, RK2018, RK2019, RK2020, RK2021,
                       RK2022, RK2023)) %>%
  mutate(year = substr(year,3,6)) %>%
  select(MSA, year, code, rank)
cca_data = merge(x=cca_data_p1, y=cca_data_p2, by=c("MSA", "year", "code")) %>%
  mutate(year = as.numeric(year)) %>%
  rename("MSA_code"="MSA","MSA"="MSA_name")

#beginning year:
BY = 2017
EY = 2023
PY = 2021



```


# Gross Regional Product Growth {data-navmenu="Economy"}


Row {data-width=150}
--------------------------------------
### Indicator
```{r}
valueBox(value = "Gross Regional Product Growth",icon = NA,caption = "Indicator - Economy",color = "lightblue")
```

### Indicator
```{r}
#devise way to code drive 
box2 = cca_data %>%
  filter(code=="E1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  mutate(value = scales::percent(value, accuracy = 0.1)) %>%
  pull(value)

valueBox(value = box2,icon = NA,caption = "MSP Region, 2023",color = "lightblue")
```

### MSP Trends
```{r}
box3a = cca_data %>%
  filter(code=="E1") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3b = cca_data %>%
  filter(code=="E1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3 = ifelse(box3b>box3a,"Improving",
              ifelse(box3b<box3a,"Worsening","Unchanged"))
box3_icon = ifelse(box3 == "Improving", "fa-arrow-up",
                   ifelse(box3 == "Worsening","fa-arrow-down","ion-code"))

valueBox(value = box3,icon = box3_icon,caption = "MSP trend from 2021", color = "lightblue")
```

### Peer Comparison
```{r}
box4_temp = cca_data %>%
  filter(code=="E1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4 = "N/A"
box4[box4_temp == 1] <- "1st Highest"
box4[box4_temp == 2] <- "2nd Highest"
box4[box4_temp == 3] <- "3rd Highest"
box4[box4_temp == 4] <- "4th Highest"
box4[box4_temp == 5] <- "5th Highest"
box4[box4_temp == 6] <- "6th Highest"
box4[box4_temp == 7] <- "7th Highest"
box4[box4_temp == 8] <- "8th Highest"
box4[box4_temp == 9] <- "9th Highest"
box4[box4_temp == 10] <- "10th Highest"
box4[box4_temp == 11] <- "11th Highest"
box4[box4_temp == 12] <- "12th Highest"

box4a = cca_data %>%
  filter(code=="E1") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4b = cca_data %>%
  filter(code=="E1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4_icon = ifelse(box4b<box4a,"fa-arrow-up",
              ifelse(box4b>box4a,"fa-arrow-down","ion-code"))

valueBox(value = box4, icon = box4_icon,caption = "out of 12 regions", color = "white")
```

Row {data-width=350}
-----------------------------------------------------------------------

### Peer Comparison Over Time

```{r}
#LINE
line_E1 = cca_data %>% 
  filter(code=="E1") %>%
  na.omit() %>%
  ggplot( aes(x=year, y=value, group=MSA, color = Legend)) +
  geom_line(aes(size=Legend)) + 
  geom_point(size = 1.8) + 
  scale_x_continuous(expand = c(0.04, 0), limits = c(BY, EY), 
                     breaks = seq(2015, 2023, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.125), 
                     breaks = seq(0, 0.125, 0.025)) +
  scale_color_manual(values=c(MSP='seagreen3', 'peer regions'='grey')) +
  scale_size_manual(values = c(MSP=1.2, no=0.8))+
  theme(
    text = element_text(family = "Lato"),
    legend.position = "none"
  )

ggplotly(line_E1, tooltip = c("year", "MSA", "value"))

```

### Peer Comparison - 2023

```{r}
#BAR
bar_E1 = cca_data %>%
  filter(code=="E1") %>%
  filter(year == EY) %>%
  ggplot(aes(x=reorder(MSA, -rank), y=value, group=MSA, fill = Legend)) + 
  geom_bar(stat="identity")  + 
  scale_fill_manual(values=c("seagreen3","grey")) +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,0.15), breaks = seq(0,0.15,0.025))+
  xlab("") +
  ylab("") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "grey"),
    panel.grid.minor = element_line(color = "grey"),
    axis.line.x = element_line(color = "grey"),
    plot.title=element_text(size=18, face = 'bold'),
    plot.subtitle=element_text(size=12, face = 'italic'),
    axis.title.y =element_text(size=12, face = 'italic', margin = margin(r = 10)),
    axis.text.x = element_text(size = 10, face = 'bold'),
    axis.text.y = element_text(size = 12, face = 'bold'),
    plot.margin = unit(c(1,1,1,1.5), "cm"),
    plot.caption = element_text(hjust = 0),
    text = element_text(family = "Lato")
  )

ggplotly(bar_E1, tooltip = c("year", "MSA", "value"))
```


# Job Growth {data-navmenu="Economy"}


Row {data-width=150}
--------------------------------------
### Indicator
```{r}
valueBox(value = "Annual Job Growth",icon = NA,caption = "Indicator - Economy",color = "lightblue")
```

### Indicator
```{r}
#devise way to code drive 
box2 = cca_data %>%
  filter(code=="E2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  mutate(value = scales::percent(value, accuracy = 0.1)) %>%
  pull(value)

valueBox(value = box2,icon = NA,caption = "MSP Region, 2023",color = "lightblue")
```

### MSP Trends
```{r}
box3a = cca_data %>%
  filter(code=="E2") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3b = cca_data %>%
  filter(code=="E2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3 = ifelse(box3b>box3a,"Improving",
              ifelse(box3b<box3a,"Worsening","Unchanged"))
box3_icon = ifelse(box3 == "Improving", "fa-arrow-up",
                   ifelse(box3 == "Worsening","fa-arrow-down","ion-code"))

valueBox(value = box3,icon = box3_icon,caption = "MSP trend from 2021", color = "lightblue")
```

### Peer Comparison
```{r}
box4_temp = cca_data %>%
  filter(code=="E2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4 = "N/A"
box4[box4_temp == 1] <- "1st Highest"
box4[box4_temp == 2] <- "2nd Highest"
box4[box4_temp == 3] <- "3rd Highest"
box4[box4_temp == 4] <- "4th Highest"
box4[box4_temp == 5] <- "5th Highest"
box4[box4_temp == 6] <- "6th Highest"
box4[box4_temp == 7] <- "7th Highest"
box4[box4_temp == 8] <- "8th Highest"
box4[box4_temp == 9] <- "9th Highest"
box4[box4_temp == 10] <- "10th Highest"
box4[box4_temp == 11] <- "11th Highest"
box4[box4_temp == 12] <- "12th Highest"

box4a = cca_data %>%
  filter(code=="E2") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4b = cca_data %>%
  filter(code=="E2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4_icon = ifelse(box4b<box4a,"fa-arrow-up",
              ifelse(box4b>box4a,"fa-arrow-down","ion-code"))

valueBox(value = box4, icon = box4_icon,caption = "out of 12 regions", color = "white")
```

Row {data-width=350}
-----------------------------------------------------------------------

### Peer Comparison Over Time

```{r}
#LINE
line_E2 = cca_data %>% 
  filter(code=="E2") %>%
  na.omit() %>%
  ggplot( aes(x=year, y=value, group=MSA, color = Legend)) +
  geom_line(aes(size=Legend)) + 
  geom_point(size = 1.8) + 
  scale_x_continuous(expand = c(0.04, 0), limits = c(BY, EY), 
                     breaks = seq(2015, 2023, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.075), 
                     breaks = seq(0, 0.075, 0.025)) +
  scale_color_manual(values=c(MSP='seagreen3', 'peer regions'='grey')) +
  scale_size_manual(values = c(MSP=1.2, no=0.8))+
  theme(
    text = element_text(family = "Lato"),
    legend.position = "none"
  )

ggplotly(line_E2, tooltip = c("year", "MSA", "value"))

```

### Peer Comparison - 2023

```{r}
#BAR
bar_E2 = cca_data %>%
  filter(code=="E2") %>%
  filter(year == EY) %>%
  ggplot(aes(x=reorder(MSA, -rank), y=value, group=MSA, fill = Legend)) + 
  geom_bar(stat="identity")  + 
  scale_fill_manual(values=c("seagreen3","grey")) +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,0.15), breaks = seq(0,0.15,0.025))+
  xlab("") +
  ylab("") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "grey"),
    panel.grid.minor = element_line(color = "grey"),
    axis.line.x = element_line(color = "grey"),
    plot.title=element_text(size=18, face = 'bold'),
    plot.subtitle=element_text(size=12, face = 'italic'),
    axis.title.y =element_text(size=12, face = 'italic', margin = margin(r = 10)),
    axis.text.x = element_text(size = 10, face = 'bold'),
    axis.text.y = element_text(size = 12, face = 'bold'),
    plot.margin = unit(c(1,1,1,1.5), "cm"),
    plot.caption = element_text(hjust = 0),
    text = element_text(family = "Lato")
  )

ggplotly(bar_E2, tooltip = c("year", "MSA", "value"))
```



# Cost-burdened Households {data-navmenu="Livability"}



Row {data-width=150}
--------------------------------------
### Indicator
```{r}
valueBox(value = "% of Households that are Cost-Burdened",icon = NA,caption = "Indicator - Livability",color = "lightblue")
```

### Indicator
```{r}
#devise way to code drive 
box2 = cca_data %>%
  filter(code=="L5") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  mutate(value = scales::percent(value, accuracy = 0.1)) %>%
  pull(value)

valueBox(value = box2,icon = NA,caption = "MSP Region, 2023",color = "lightblue")
```

### MSP Trends
```{r}
box3a = cca_data %>%
  filter(code=="L5") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3b = cca_data %>%
  filter(code=="L5") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3 = ifelse(box3b>box3a,"Improving",
              ifelse(box3b<box3a,"Worsening","Unchanged"))
box3_icon = ifelse(box3 == "Improving", "fa-arrow-up",
                   ifelse(box3 == "Worsening","fa-arrow-down","ion-code"))

valueBox(value = box3,icon = box3_icon,caption = "MSP trend from 2021", color = "lightblue")
```

### Peer Comparison
```{r}
box4_temp = cca_data %>%
  filter(code=="L5") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4 = "N/A"
box4[box4_temp == 1] <- "1st Lowest"
box4[box4_temp == 2] <- "2nd Lowest"
box4[box4_temp == 3] <- "3rd Lowest"
box4[box4_temp == 4] <- "4th Lowest"
box4[box4_temp == 5] <- "5th Lowest"
box4[box4_temp == 6] <- "6th Lowest"
box4[box4_temp == 7] <- "7th Lowest"
box4[box4_temp == 8] <- "8th Lowest"
box4[box4_temp == 9] <- "9th Lowest"
box4[box4_temp == 10] <- "10th Lowest"
box4[box4_temp == 11] <- "11th Lowest"
box4[box4_temp == 12] <- "12th Lowest"

box4a = cca_data %>%
  filter(code=="L5") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4b = cca_data %>%
  filter(code=="L5") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4_icon = ifelse(box4b<box4a,"fa-arrow-up",
              ifelse(box4b>box4a,"fa-arrow-down","ion-code"))

valueBox(value = box4, icon = box4_icon,caption = "out of 12 regions", color = "white")
```

Row {data-width=350}
-----------------------------------------------------------------------

### Peer Comparison Over Time

```{r}
#LINE
line_L5 = cca_data %>% 
  filter(code=="L5") %>%
  na.omit() %>%
  ggplot( aes(x=year, y=value, group=MSA, color = Legend)) +
  geom_line(aes(size=Legend)) + 
  geom_point(size = 1.8) + 
  scale_x_continuous(expand = c(0.04, 0), limits = c(BY, EY), 
                     breaks = seq(2015, 2023, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.5), 
                     breaks = seq(0, 0.5, 0.1)) +
  scale_color_manual(values=c(MSP='seagreen3', 'peer regions'='grey')) +
  scale_size_manual(values = c(MSP=1.2, no=0.8))+
  theme(
    text = element_text(family = "Lato"),
    legend.position = "none"
  )

ggplotly(line_L5, tooltip = c("year", "MSA", "value"))

```

### Peer Comparison - 2023

```{r}
#BAR
bar_L5 = cca_data %>%
  filter(code=="L5") %>%
  filter(year == EY) %>%
  ggplot(aes(x=reorder(MSA, -rank), y=value, group=MSA, fill = Legend)) + 
  geom_bar(stat="identity")  + 
  scale_fill_manual(values=c("seagreen3","grey")) +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,0.5), breaks = seq(0,0.5,0.1))+
  xlab("") +
  ylab("") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "grey"),
    panel.grid.minor = element_line(color = "grey"),
    axis.line.x = element_line(color = "grey"),
    plot.title=element_text(size=18, face = 'bold'),
    plot.subtitle=element_text(size=12, face = 'italic'),
    axis.title.y =element_text(size=12, face = 'italic', margin = margin(r = 10)),
    axis.text.x = element_text(size = 10, face = 'bold'),
    axis.text.y = element_text(size = 12, face = 'bold'),
    plot.margin = unit(c(1,1,1,1.5), "cm"),
    plot.caption = element_text(hjust = 0),
    text = element_text(family = "Lato")
  )

ggplotly(bar_L5, tooltip = c("year", "MSA", "value"))
```


# Change in Median Rent {data-navmenu="Livability"}


Row {data-width=150}
--------------------------------------
### Indicator
```{r}
valueBox(value = "Change in Median Rent (2-BR Apt.)",icon = NA,caption = "Indicator - Livability",color = "lightblue")
```

### Indicator
```{r}
#devise way to code drive 
box2 = cca_data %>%
  filter(code=="L6") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  mutate(value = scales::percent(value, accuracy = 0.1)) %>%
  pull(value)

valueBox(value = box2,icon = NA,caption = "MSP Region, 2023",color = "lightblue")
```

### MSP Trends
```{r}
box3a = cca_data %>%
  filter(code=="L6") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3b = cca_data %>%
  filter(code=="L6") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3 = ifelse(box3b>box3a,"Improving",
              ifelse(box3b<box3a,"Worsening","Unchanged"))
box3_icon = ifelse(box3 == "Improving", "fa-arrow-up",
                   ifelse(box3 == "Worsening","fa-arrow-down","ion-code"))

valueBox(value = box3,icon = box3_icon,caption = "MSP trend from 2021", color = "lightblue")
```

### Peer Comparison
```{r}
box4_temp = cca_data %>%
  filter(code=="L6") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4 = "N/A"
box4[box4_temp == 1] <- "1st Lowest"
box4[box4_temp == 2] <- "2nd Lowest"
box4[box4_temp == 3] <- "3rd Lowest"
box4[box4_temp == 4] <- "4th Lowest"
box4[box4_temp == 5] <- "5th Lowest"
box4[box4_temp == 6] <- "6th Lowest"
box4[box4_temp == 7] <- "7th Lowest"
box4[box4_temp == 8] <- "8th Lowest"
box4[box4_temp == 9] <- "9th Lowest"
box4[box4_temp == 10] <- "10th Lowest"
box4[box4_temp == 11] <- "11th Lowest"
box4[box4_temp == 12] <- "12th Lowest"

box4a = cca_data %>%
  filter(code=="L6") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4b = cca_data %>%
  filter(code=="L6") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4_icon = ifelse(box4b<box4a,"fa-arrow-up",
              ifelse(box4b>box4a,"fa-arrow-down","ion-code"))

valueBox(value = box4, icon = box4_icon,caption = "out of 12 regions", color = "white")
```
Row {data-width=350}
-----------------------------------------------------------------------

### Peer Comparison Over Time

```{r}
#LINE
line_L6 = cca_data %>% 
  filter(code=="L6") %>%
  na.omit() %>%
  ggplot( aes(x=year, y=value, group=MSA, color = Legend)) +
  geom_line(aes(size=Legend)) + 
  geom_point(size = 1.8) + 
  scale_x_continuous(expand = c(0.04, 0), limits = c(BY, EY), 
                     breaks = seq(2015, 2023, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 0.10), 
                     breaks = seq(0, 0.10, 0.025)) +
  scale_color_manual(values=c(MSP='seagreen3', 'peer regions'='grey')) +
  scale_size_manual(values = c(MSP=1.2, no=0.8))+
  theme(
    text = element_text(family = "Lato"),
    legend.position = "none"
  )

ggplotly(line_L6, tooltip = c("year", "MSA", "value"))

```

### Peer Comparison - 2023

```{r}
#BAR
bar_L6 = cca_data %>%
  filter(code=="L6") %>%
  filter(year == EY) %>%
  ggplot(aes(x=reorder(MSA, -rank), y=value, group=MSA, fill = Legend)) + 
  geom_bar(stat="identity")  + 
  scale_fill_manual(values=c("seagreen3","grey")) +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,0.15), breaks = seq(0,0.15,0.025))+
  xlab("") +
  ylab("") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "grey"),
    panel.grid.minor = element_line(color = "grey"),
    axis.line.x = element_line(color = "grey"),
    plot.title=element_text(size=18, face = 'bold'),
    plot.subtitle=element_text(size=12, face = 'italic'),
    axis.title.y =element_text(size=12, face = 'italic', margin = margin(r = 10)),
    axis.text.x = element_text(size = 10, face = 'bold'),
    axis.text.y = element_text(size = 12, face = 'bold'),
    plot.margin = unit(c(1,1,1,1.5), "cm"),
    plot.caption = element_text(hjust = 0),
    text = element_text(family = "Lato")
  )

ggplotly(bar_L6, tooltip = c("year", "MSA", "value"))
```



# Gross Regional Product {data-navmenu="Vital Stats"}

Row {data-width=150}
--------------------------------------
### Indicator
```{r}
valueBox(value = "Gross Regional Product (Millions)",icon = NA,caption = "Indicator - Vital Statistics",color = "lightblue")
```

### Indicator
```{r}
#devise way to code drive 
box2 = cca_data %>%
  filter(code=="V1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  mutate(value = scales::percent(value, accuracy = 0.1)) %>%
  pull(value)

valueBox(value = box2,icon = NA,caption = "MSP Region, 2023",color = "lightblue")
```

### MSP Trends
```{r}
box3a = cca_data %>%
  filter(code=="V1") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3b = cca_data %>%
  filter(code=="V1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3 = ifelse(box3b>box3a,"Improving",
              ifelse(box3b<box3a,"Worsening","Unchanged"))
box3_icon = ifelse(box3 == "Improving", "fa-arrow-up",
                   ifelse(box3 == "Worsening","fa-arrow-down","ion-code"))

valueBox(value = box3,icon = box3_icon,caption = "MSP trend from 2021", color = "lightblue")
```

### Peer Comparison
```{r}
box4_temp = cca_data %>%
  filter(code=="V1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4 = "N/A"
box4[box4_temp == 1] <- "1st Highest"
box4[box4_temp == 2] <- "2nd Highest"
box4[box4_temp == 3] <- "3rd Highest"
box4[box4_temp == 4] <- "4th Highest"
box4[box4_temp == 5] <- "5th Highest"
box4[box4_temp == 6] <- "6th Highest"
box4[box4_temp == 7] <- "7th Highest"
box4[box4_temp == 8] <- "8th Highest"
box4[box4_temp == 9] <- "9th Highest"
box4[box4_temp == 10] <- "10th Highest"
box4[box4_temp == 11] <- "11th Highest"
box4[box4_temp == 12] <- "12th Highest"

box4a = cca_data %>%
  filter(code=="V1") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4b = cca_data %>%
  filter(code=="V1") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4_icon = ifelse(box4b<box4a,"fa-arrow-up",
              ifelse(box4b>box4a,"fa-arrow-down","ion-code"))

valueBox(value = box4, icon = box4_icon,caption = "out of 12 regions", color = "white")
```
Row {data-width=350}
-----------------------------------------------------------------------

### Peer Comparison Over Time

```{r}
#LINE
line_V1 = cca_data %>% 
  filter(code=="V1") %>%
  na.omit() %>%
  ggplot( aes(x=year, y=value, group=MSA, color = Legend)) +
  geom_line(aes(size=Legend)) + 
  geom_point(size = 1.8) + 
  scale_x_continuous(expand = c(0.04, 0), limits = c(BY, EY), 
                     breaks = seq(2015, 2023, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 800000), 
                     breaks = seq(0, 800000, 200000)) +
  scale_color_manual(values=c(MSP='seagreen3', 'peer regions'='grey')) +
  scale_size_manual(values = c(MSP=1.2, no=0.8))+
  theme(
    text = element_text(family = "Lato"),
    legend.position = "none"
  )

ggplotly(line_V1, tooltip = c("year", "MSA", "value"))

```

### Peer Comparison - 2023

```{r}
#BAR
bar_V1 = cca_data %>%
  filter(code=="V1") %>%
  filter(year == EY) %>%
  ggplot(aes(x=reorder(MSA, -rank), y=value, group=MSA, fill = Legend)) + 
  geom_bar(stat="identity")  + 
  scale_fill_manual(values=c("seagreen3","grey")) +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,800000), breaks = seq(0,800000,200000))+
  xlab("") +
  ylab("") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "grey"),
    panel.grid.minor = element_line(color = "grey"),
    axis.line.x = element_line(color = "grey"),
    plot.title=element_text(size=18, face = 'bold'),
    plot.subtitle=element_text(size=12, face = 'italic'),
    axis.title.y =element_text(size=12, face = 'italic', margin = margin(r = 10)),
    axis.text.x = element_text(size = 10, face = 'bold'),
    axis.text.y = element_text(size = 12, face = 'bold'),
    plot.margin = unit(c(1,1,1,1.5), "cm"),
    plot.caption = element_text(hjust = 0),
    text = element_text(family = "Lato")
  )

ggplotly(bar_V1, tooltip = c("year", "MSA", "value"))
```


# Gross Regional Product per Capita {data-navmenu="Vital Stats"}


Row {data-width=150}
--------------------------------------
### Indicator
```{r}
valueBox(value = "Gross Regional Product per Capita",icon = NA,caption = "Indicator - Vital Statistics",color = "lightblue")
```

### Indicator
```{r}
#devise way to code drive 
box2 = cca_data %>%
  filter(code=="V2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)

valueBox(value = box2,icon = NA,caption = "MSP Region, 2023",color = "lightblue")
```

### MSP Trends
```{r}
box3a = cca_data %>%
  filter(code=="V2") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3b = cca_data %>%
  filter(code=="V2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(value)
box3 = ifelse(box3b>box3a,"Improving",
              ifelse(box3b<box3a,"Worsening","Unchanged"))
box3_icon = ifelse(box3 == "Improving", "fa-arrow-up",
                   ifelse(box3 == "Worsening","fa-arrow-down","ion-code"))

valueBox(value = box3,icon = box3_icon,caption = "MSP trend from 2021", color = "lightblue")
```

### Peer Comparison
```{r}
box4_temp = cca_data %>%
  filter(code=="V2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4 = "N/A"
box4[box4_temp == 1] <- "1st Highest"
box4[box4_temp == 2] <- "2nd Highest"
box4[box4_temp == 3] <- "3rd Highest"
box4[box4_temp == 4] <- "4th Highest"
box4[box4_temp == 5] <- "5th Highest"
box4[box4_temp == 6] <- "6th Highest"
box4[box4_temp == 7] <- "7th Highest"
box4[box4_temp == 8] <- "8th Highest"
box4[box4_temp == 9] <- "9th Highest"
box4[box4_temp == 10] <- "10th Highest"
box4[box4_temp == 11] <- "11th Highest"
box4[box4_temp == 12] <- "12th Highest"

box4a = cca_data %>%
  filter(code=="V2") %>%
  filter(year == PY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4b = cca_data %>%
  filter(code=="V2") %>%
  filter(year == EY) %>%
  filter(MSA == "MSP") %>%
  pull(rank)
box4_icon = ifelse(box4b<box4a,"fa-arrow-up",
              ifelse(box4b>box4a,"fa-arrow-down","ion-code"))

valueBox(value = box4, icon = box4_icon,caption = "out of 12 regions", color = "white")
```
Row {data-width=350}
-----------------------------------------------------------------------

### Peer Comparison Over Time

```{r}
#LINE
line_V2 = cca_data %>% 
  filter(code=="V2") %>%
  na.omit() %>%
  ggplot( aes(x=year, y=value, group=MSA, color = Legend)) +
  geom_line(aes(size=Legend)) + 
  geom_point(size = 1.8) + 
  scale_x_continuous(expand = c(0.04, 0), limits = c(BY, EY), 
                     breaks = seq(2015, 2023, 1)) + 
  scale_y_continuous(expand = c(0, 0), limits = c(0, 150000), 
                     breaks = seq(0, 150000, 25000)) +
  scale_color_manual(values=c(MSP='seagreen3', 'peer regions'='grey')) +
  scale_size_manual(values = c(MSP=1.2, no=0.8))+
  theme(
    text = element_text(family = "Lato"),
    legend.position = "none"
  )

ggplotly(line_V2, tooltip = c("year", "MSA", "value"))

```

### Peer Comparison - 2023

```{r}
#BAR
bar_V2 = cca_data %>%
  filter(code=="V2") %>%
  filter(year == EY) %>%
  ggplot(aes(x=reorder(MSA, -rank), y=value, group=MSA, fill = Legend)) + 
  geom_bar(stat="identity")  + 
  scale_fill_manual(values=c("seagreen3","grey")) +
  coord_flip() +
  scale_x_discrete(labels = function(x) str_wrap(x, width = 30)) +
  scale_y_continuous(labels = scales::percent, limits = c(0,150000), breaks = seq(0,150000,25000))+
  xlab("") +
  ylab("") +
  theme(
    plot.background = element_rect(fill = "white"),
    panel.background = element_rect(fill = "white"),
    panel.grid.major = element_line(color = "grey"),
    panel.grid.minor = element_line(color = "grey"),
    axis.line.x = element_line(color = "grey"),
    plot.title=element_text(size=18, face = 'bold'),
    plot.subtitle=element_text(size=12, face = 'italic'),
    axis.title.y =element_text(size=12, face = 'italic', margin = margin(r = 10)),
    axis.text.x = element_text(size = 10, face = 'bold'),
    axis.text.y = element_text(size = 12, face = 'bold'),
    plot.margin = unit(c(1,1,1,1.5), "cm"),
    plot.caption = element_text(hjust = 0),
    text = element_text(family = "Lato")
  )

ggplotly(bar_V2, tooltip = c("year", "MSA", "value"))
```


